### 2016-05-19 misc/notes.tex
enforce 90-character code width
added derivation of probability formula in pair-compute.py

If we have a set of $R$ lattice sites indexed by $(b,\l,m,n)$ mutually
satisfying (\ref{condA0}) and (\ref{condB0}), then the probability of
filling exactly $r$ of them with $^{13}$C nuclei is
\begin{align}
  P_{R,r}=p^r\p{1-p}^{R-r}\m{R\\r}=\f{R!~p^r\p{1-p}^{R-r}}{r!\p{R-r}!},
\end{align}
where $p$ is the probability that any particular site with a $^{13}$C
nucleus, i.e. the relative abundance of $^{13}$C. The probability of
having at least two $^{13}$C nuclei in these sites is therefore
\begin{align}
  P_{R,r\ge2}=\sum_{r=2}^RP_{R,r}=1-\p{P_{R,0}+P_{R,1}}.
\end{align}
If we have many such sets of lattice sites, then the total probability
$\bar P$ of having at least two sites filled within at least one set
of sites is
\begin{align}
  \bar P=1-\prod_R\p{1-P_{R,r\ge2}} =1-\prod_R\p{P_{R,0}+P_{R,1}}
  =1-\prod_R\p{1-p}^R\p{1+\f{Rp}{1-p}}.
\end{align}

>>>>

Let $p$ denote the isotopic abundance of $^{13}$C, and consider a set
$R$ of diamond lattice sites mutually satisfying (\ref{condA0}) and
(\ref{condB0}). If there are $N$ ways of filling exactly 2 out of the
lattice sites in $R$ with $^{13}$C nuclei in such a way that both
$^{13}$C nuclear spins are addressable, the probability of doing so is
\begin{align}
  P_{R,2}=p^2\p{1-p}^{\abs{R}-2}N.
\end{align}
Though there are $\m{\abs{R}\\2}$ ways total of filling the lattice
sites in $R$ with exactly 2 nuclei, in some of these configurations
the perpendicular components of the hyperfine fields (i.e.
$\v A_j^\perp$) for these nuclei are mutually parallel, which makes
the spins of these nuclei unaddressable. If there is a subset
$S_R\subset R$ of lattice sites within which the $\v A_j^\perp$ for
all lattice sites $s_j\in S_R$ are mutually parallel, then there are
$\m{\abs{S_R}\\2}$ configurations out of the $\m{\abs{R}\\2}$ which
must be excluded in the counting of $N$; therefore,
\begin{align}
  P_{R,2}=p^2\p{1-p}^{\abs{R}-2}
  \sp{\m{\abs{R}\\2}-\sum_{S_R}\m{\abs{S_R}\\2}}.
\end{align}
The total probability $\bar P$ of finding at least one pair of
addressable $^{13}$C nuclear spins in an NV system with multiple sets
of larmor equal lattice sites is therefore
\begin{align}
  \bar P=1-\prod_R\p{1-P_{R,2}}
  =1-\prod_R\p{1-p^2\p{1-p}^{\abs{R}-2}
  \sp{\m{\abs{R}\\2}-\sum_{S_R}\m{\abs{S_R}\\2}}},
\end{align}
where the product over $R$ excludes sets of lattice sites at which
individual nuclei are unaddressable (i.e. lattice sites along the
natural NV axis $\uv z$, and lattice sites $\v s$ for which
$\v s\c\uv z=0$).
